% !TeX root = link_prediction_for_diffusion_kernels.tex


\definecolor{cadetgrey}{rgb}{0.8721875,0.8721875,0.8721875}
\newcolumntype{g}{>{\columncolor{cadetgrey}}c}

{\setlength{\extrarowheight}{2pt}
\begin{table*}[!htbp]
\vspace*{-0.5cm}
\centering
\caption{\textit {Predictive performance on 14 gene-disease associations using four different networks induced by the BioGPS, Biogridphys, Hprd and Omim. We report the average AUC-ROC (\%) and standard deviations for all difussion-based kernels with (+) and without (-) link enrichment.}}
\label{table:results1}
\setlength{\tabcolsep}{0.6mm}
\begin{tabular}{|c|c|g|c|g|c|g|c|g|}
\hline
 & \multicolumn{2}{c|}{\textbf{BioGPS}} & \multicolumn{2}{c|}{\textbf{Biogridphys}} & \multicolumn{2}{c|}{\textbf{Hprd}} & \multicolumn{2}{c|}{\textbf{Omim}}\\
 \hline
Disease & - & + & - & + & - & + & - & + \\
\hline
1 & 60.3$\pm$1.5 & 63.4$\pm$1.0 & 73.1$\pm$4.1 & 77.1$\pm$2.9 & 75.5$\pm$0.2 & 77.5$\pm$0.9 & 85.3$\pm$1.1 & 86.9$\pm$1.5 \\
2 & 53.7$\pm$1.4 & 63.4$\pm$3.8 & 56.6$\pm$3.4 & 61.3$\pm$4.1 & 57.1$\pm$0.9 & 60.2$\pm$1.8 & 75.0$\pm$2.2 & 76.5$\pm$2.4 \\
3 & 50.2$\pm$0.4 & 58.6$\pm$3.0 & 58.9$\pm$5.9 & 67.5$\pm$7.7 & 61.8$\pm$3.6 & 70.7$\pm$3.8 & 77.3$\pm$1.8 & 83.1$\pm$0.9 \\
4 & 61.5$\pm$0.9 & 72.2$\pm$2.2 & 65.7$\pm$4.1 & 74.6$\pm$4.2 & 67.3$\pm$1.1 & 71.9$\pm$2.2 & 90.2$\pm$1.2 & 92.1$\pm$1.2 \\
5 & 55.1$\pm$0.4 & 61.7$\pm$0.9 & 54.2$\pm$4.8 & 60.7$\pm$4.0 & 57.7$\pm$1.6 & 67.0$\pm$1.8 & 76.4$\pm$0.8 & 81.9$\pm$1.5 \\
6 & 60.8$\pm$0.9 & 67.9$\pm$2.2 & 60.6$\pm$3.6 & 65.9$\pm$3.5 & 66.8$\pm$1.3 & 71.9$\pm$2.3 & 79.9$\pm$2.4 & 83.3$\pm$1.2 \\
7 & 68.1$\pm$1.4 & 73.4$\pm$0.7 & 57.7$\pm$3.2 & 63.7$\pm$4.0 & 68.9$\pm$2.1 & 72.5$\pm$1.2 & 81.0$\pm$1.2 & 84.1$\pm$1.0 \\
8 & 69.2$\pm$2.3 & 74.0$\pm$2.2 & 68.1$\pm$3.6 & 72.6$\pm$2.5 & 76.6$\pm$2.2 & 80.3$\pm$2.8 & 85.4$\pm$2.2 & 91.0$\pm$1.0 \\
9 & 62.0$\pm$1.6 & 64.5$\pm$1.4 & 68.7$\pm$4.6 & 71.7$\pm$4.3 & 68.4$\pm$2.5 & 75.0$\pm$3.2 & 78.5$\pm$0.2 & 80.6$\pm$0.6 \\
10 & 67.5$\pm$2.9 & 72.9$\pm$1.8 & 58.8$\pm$3.2 & 66.1$\pm$3.8 & 65.8$\pm$3.4 & 74.4$\pm$2.6 & 86.1$\pm$0.6 & 87.8$\pm$0.3 \\
11 & 58.7$\pm$1.8 & 62.3$\pm$1.5 & 58.2$\pm$1.2 & 61.6$\pm$1.7 & 60.1$\pm$1.1 & 64.2$\pm$1.5 & 82.0$\pm$1.4 & 83.6$\pm$0.9 \\
12 & 64.0$\pm$1.3 & 73.6$\pm$1.7 & 59.3$\pm$2.1 & 67.0$\pm$2.8 & 60.8$\pm$1.1 & 68.8$\pm$2.8 & 82.0$\pm$1.8 & 85.9$\pm$1.7 \\
13 & 56.5$\pm$0.9 & 63.3$\pm$2.4 & 55.8$\pm$1.1 & 65.1$\pm$4.2 & 66.4$\pm$1.3 & 71.8$\pm$1.7 & 83.1$\pm$2.8 & 87.5$\pm$2.5 \\
14 & 55.2$\pm$0.3 & 62.3$\pm$1.2 & 55.6$\pm$1.6 & 63.5$\pm$4.0 & 66.3$\pm$2.3 & 71.1$\pm$2.8 & 97.4$\pm$0.1 & 99.0$\pm$0.4 \\
\hline
$\overline{AUC}$ & 60.2$\pm$0.3 & 66.7$\pm$1.2 & 60.8$\pm$1.6 & 67.0$\pm$4.0 & 65.7$\pm$2.3 & 71.2$\pm$2.8 & 82.8$\pm$0.1 & 86.0$\pm$0.4 \\
\hline
\end{tabular}
\end{table*}

\section{Results and Discussion}
\label{results-discussion}

In Table \ref{table:results1} we report a synthesis of all the experiments.
Each row represent a different disease, in the columns we consider the
different sources of information used to build the underlying network (BioGPS,
Biogridphys, Hprd, Omim). Note that each resource yields a graph with
different characteristic sparsity and number of components. We compare the
average AUC-ROC scores in two cases: plain diffusion kernel (denoted by a "-"
symbol) and diffusion kernel on a modified network $G'$ (denoted by a "+"
symbol) which includes the novel edges identified by a link prediction system.
Here we report the aggregated results (a detailed breakdown is available in
the \textit{Appendix}\footnote{https://github.com/dinhinfotech/ICANN/blob/mast
er/appendix.pdf}) where we have averaged not only across a random choice of
negative genes, but also among the type of diffusion kernel and the type of
link prediction. The noteworthy result is how consistent the result is: each
link prediction method improves each diffusion kernel algorithm, and on
average using link prediction yields a 15\% to 20\% relative error reduction
for diffusion-based methods. What varies is the amount of improvement, which
depends on the coupling between the four elements: the disease, the
information source, the link prediction method and the diffusion kernel
algorithm. In specific we obtain that the largest improvement is obtained for
disease 3 (connective) where we have a maximum improvement of 20\% ROC points,
while the minimum improvement is for disease 8 (immunological) with a minimal
improvement of 0\% ROC points. On average the largest improvement is of 13\%
ROC points, while the smallest improvement is on average of 1\% ROC point.
Such stable results are of interest since diffusion-based methods are
currently state-of-the-art for gene-disease prioritization tasks, and hence a
technique that can offer a consistent and relatively large improvement can have
important practical consequences in the understanding of disease mechanisms.

\section{Conclusion and Future Work}
\label{conclusion}

% what is the contribution that is not trivial

In this paper we have proposed the notion of {\em link enrichment} for
diffusion kernels, that is, the idea of carrying out the computation of
information diffusion on a network that contains edges identified by link
prediction approaches. We have discovered a surprisingly robust signal that
indicates that diffusion-based node kernels consistently benefit from the
coupling with similarity-based link prediction techniques on large
scale datasets in biological domains.

In future work we will carry out a more fine grained analysis, defining a
taxonomy of prediction problems on networks that make use of the notion of
node similarity and analyze which link prediction strategies can be
effectively coupled with specific node similarity computation techniques for
a given problem class. In addition we will study the quantitative
relation between the degree of missingness and the size of the improvement
offered by prepending the link prediction to the node similarity assessment.
Finally, we will extend the analysis to the more complex case of kernel
integration and data fusion, i.e. when multiple heterogeneous information
sources are used jointly to define the predictive task.